Evolution of CSMA Protocols fro the IEEE 802.11 Standard

### 2013-01-22 paper.tex
new title, new paper

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Battling the MAC Bottleneck in IEEE 802.11 WLANs}

@@

\begin{abstract}
%\boldmath
As the physical layer (PHY) data rates increase and wireless local area network (WLAN) frames become shorter, the medium access control (MAC) overheads account for a larger fraction of the total transmission time.
This problem is known as the MAC bottleneck because it limits the throughput available to the user no matter how advanced PHY techniques are used.
Current standardization efforts circumvent the problem by using aggregation.
By aggregating multiple network packets in a single MAC layer frame, the MAC overhead per useful network layer bit is reduced.

CSMA/ECA is an evolution of the well known CSMA/CA protocol that reduces the MAC contention overhead and therefore helps in battling the MAC bottleneck problem.
The core idea is the use of a deterministic backoff after successful transmissions.
In this paper we provide a survey of all the related contributions in the last years and describe the algorithm that can reach collision-free operation even for a large number of contenders.
We present simulation results to quantify the potential performance gains.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

\hfill mds

\hfill January 11, 2007

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Evolution of CSMA Protocols fro the IEEE 802.11 Standard}

@@

\begin{abstract}
%\boldmath
In this paper we present the requirements of candidate protocols to replace the pervasive CSMA/CA medium access control.
We discuss the possibility of further preventing collisions and provide an overview of the related work.
We specify protocols that are candidates of replacing CSMA/CA in pseudocode and use simulation to assess performance metrics such as throughput, fairness and collision probability.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

A candidate to replace CSMA/CA should 
\begin{itemize}
  \item Provide performance advantages, either in the form of throughput or short term fairness.
  \item Be backward compatible with current implementation.
  \item Be simple a simple evolution implementation to ease the transition and reduce time to market (Optional but desirable).
\end{itemize}
\section{Related Work}

\section{Enhanced CSMA}

\section{Performance Evaluation}
